Computer Science House By-Laws

### 2017-06-20 articles.tex
Removed all trailing whitespacs from .tex files
Fix Git Revision Insertion for Makefile (#108)

Fixed periods and capitalization

Add more instructions to readme

ran script to add periods to end of any bullet points

removed all periods at end of \item

removed periods

maunally edited the punctuation

ran script to add periods to end of any bullet points

removed all periods at end of \item

removed periods

maunally edited the punctuation

\asection{House Objectives}
The objectives of Computer Science House are:
\begin{enumerate}
	\item To enhance the education experience of its members.
	\item To offer students educational programming with an emphasis in computers.
	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community.
	\item To provide a friendly and comfortable living environment in the residence halls.
\end{enumerate}

@@

\asubsection{Maintainer Expectations}
Maintainers are expected to:
\begin{itemize}
	\item Review changes to the Constitution for grammar, spelling, and internal consistency.
	\item Keep a public record of changes to the Constitution.
	\item Participate in discussion of proposals.
	\item Facilitate the creation of new changes to the Constitution by other members.
	\item Be knowledgeable about the Constitution.
\end{itemize}
Failure to meet any of these expectations is grounds for revocation of Maintainer status by the Executive Board.

@@

% ARTICLE III - MEMBERSHIP
\article{Membership}
There are five major types of membership available to Computer Science House.
Each carries different qualifications, expectations, and privileges.
When describing the different memberships available, the following terms are used:
\begin{description}
	\item[Qualifications:] What qualifications an applicant needs to apply.
	\item[Selection:] The process by which an applicant gains membership.
	\item[Expectations:] The duties and responsibilities of House members.
	\item[Privileges:] The benefits offered to House members.
	\item[Evaluations:] The process by which a member is reviewed and assessed.
	\item[Leave of Absence:] The process by which a member may leave House for a period of time.
	\item[Resignations:] The process by which a member terminates House membership.
	\item[Term:] The length of time the membership lasts.
\end{description}

@@

% ARTICLE IV - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairman.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad-hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairman
	\item House Secretary
	\item Ad Hoc Director (s)
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.

\asection{Responsibilities}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House.
	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House.
	\item To report pertinent information to House members at the following House Meeting.
	\item To maintain records of the goals defined by each previous Executive Board.
	\item To act as a Judicial Board as defined in \ref{Judicial}.
	\item To review major projects, as defined in \ref{Expectations of House Members}, presented to them by the Evaluations director.
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board.
	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.
		The constitution should remain up to date with current practices.
\end{enumerate}

\asubsection{Responsibilities of the Chairman}
\begin{enumerate}
	\item To preside over Executive Board and House Meetings.
	\item To exercise general supervision over the operations of the Executive Board.
	\item To exercise general supervision over regular House activities.
	\item To act as a liaison to the academic and administrative departments at RIT.
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
	\item To cast tie-breaking vote in a split decision in an Executive Board vote.
\end{enumerate}

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
	\item To preside over Evaluations Meetings.
	\item To exercise general supervision over Evaluations operations.
	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members.
	\item To oversee the Semi-Annual Evaluations of current House members.
	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency.
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
	\item To prepare the House for Open Houses, tours, and special events.
\end{enumerate}

\asubsection{Responsibilities of the Social Director}
\begin{enumerate}
	\item To preside over Social Meetings.
		House members are encouraged to bring ideas for social events to the meetings for discussion.
	\item To exercise general supervision over Social operations.
	\item To oversee the organization, initiation, and execution of House activities and events.
	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year.
\end{enumerate}

\asubsection{Responsibilities of the Financial Director}
\begin{enumerate}
	\item To preside over Financial Meetings.
		House members are encouraged to bring ideas for fund-raising activities to the meetings for discussion.
	\item To supervise financial administrators and transactions involving house projects.
	\item To maintain financial and inventory records of House capital and assets.
	\item To plan and enforce a House budget.
	\item To oversee House finances and generation of House funds.
	\item To publish a semesterly House financial statement.
	\item To supervise the collection of semesterly House dues.
	\item To oversee the planning and execution of fundraising events.
\end{enumerate}

\asubsection{Responsibilities of the Research and Development Director}
\begin{enumerate}
	\item To preside over Research and Development Meetings.
		House members are encouraged to bring ideas for projects to the meetings for discussion.
	\item To exercise general supervision over Research and Development operations.
	\item To oversee the planning, organization and construction of technical projects for the House's benefit.
	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment.
	\item To provide seminars and tutorials to educate House members in technical areas.
\end{enumerate}

\asubsection{Responsibilities of the House Improvements Director}
\begin{enumerate}
	\item To preside over House Improvements Meetings.
	\item To exercise general supervision over the House Improvements operations.
	\item To oversee the organization and construction of physical improvements to the House.
	\item To oversee the general maintenance of the appearance of the House.
\end{enumerate}

\asubsection{Responsibilities of the Operational Communications Director}
\begin{enumerate}
	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings.
	\item To report the status of the House computer systems and network to the Executive Board and House members.
\end{enumerate}

\asubsection{Responsibilities of the House History Director}
\begin{enumerate}
	\item To preside over House History Meetings.
	\item To exercise general supervision over the House History operations.
	\item To maintain, uphold, and promote house traditions.
	\item To collaborate with the Social Director(s) to ensure that all the Active, Alumni, and Advisory Members are informed of upcoming events.
	\item To oversee the production and distribution of a semi-annual newsletter.
	\item To oversee the creation of a yearbook outlining House events for the year.
\end{enumerate}

\asubsection{Responsibilities of the House Secretary}
\begin{enumerate}
	\item To ensure that minutes are recorded and posted for Executive Board Meetings.
	\item To ensure that minutes are recorded and posted for House Meetings.
	\item To oversee the maintenance of Executive Board records and documents.
	\item To provide administrative assistance to the Executive Board.
	\item To oversee the maintenance of the Activities Information Centers.
	\item To record all votes cast during House Meetings and Open Executive Board Meetings.
\end{enumerate}

\asubsection{Responsibilities of Ad Hoc Directorships}
\begin{enumerate}
	\item Ad-Hoc Directorships are responsible for the task for which they were created.
	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director.
\end{enumerate}

\asection{Qualifications}
\asubsection{Qualifications to be the Chairman, Evaluations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office.
	\item Candidates must reside on floor during the term of office.
	\item Candidates must have at least one full semester of House membership as an Active Member.
	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairman, should they be elected.
\end{enumerate}
\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office.
	\item Candidates must have at least one full semester of House membership as an Active Member.
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
\end{enumerate}
\asubsection{Qualifications to be the Operational Communications Director}
\begin{enumerate}
	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
	\item Candidates must be a current Active Member.
	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
\end{enumerate}

\asubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
\begin{enumerate}
\item Candidates must be Active Members.
\end{enumerate}

>>>>

\asection{House Objectives}
The objectives of Computer Science House are:
\begin{enumerate}
	\item To enhance the education experience of its members
	\item To offer students educational programming with an emphasis in computers
	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community
	\item To provide a friendly and comfortable living environment in the residence halls
\end{enumerate}

@@

\asubsection{Maintainer Expectations}
Maintainers are expected to:
\begin{itemize}
	\item Review changes to the Constitution for grammar, spelling, and internal consistency
	\item Keep a public record of changes to the Constitution
	\item Participate in discussion of proposals
	\item Facilitate the creation of new changes to the Constitution by other members
	\item Be knowledgeable about the Constitution
\end{itemize}
Failure to meet any of these expectations is grounds for revocation of Maintainer status by the Executive Board.

@@

% ARTICLE III - MEMBERSHIP
\article{Membership}
There are five major types of membership available to Computer Science House.
Each carries different qualifications, expectations, and privileges.
When describing the different memberships available, the following terms are used:
\begin{description}
	\item[Qualifications:] What qualifications an applicant needs to apply
	\item[Selection:] The process by which an applicant gains membership
	\item[Expectations:] The duties and responsibilities of House members
	\item[Privileges:] The benefits offered to House members
	\item[Evaluations:] The process by which a member is reviewed and assessed
	\item[Leave of Absence:] The process by which a member may leave House for a period of time
	\item[Resignations:] The process by which a member terminates House membership
	\item[Term:] The length of time the membership lasts
\end{description}

@@

% ARTICLE IV - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairman.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad-hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairman
	\item House Secretary
	\item Ad Hoc Director(s)
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.

\asection{Responsibilities}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
	\item To report pertinent information to House members at the following House Meeting
	\item To maintain records of the goals defined by each previous Executive Board
	\item To act as a Judicial Board as defined in \ref{Judicial}
	\item To review major projects, as defined in \ref{Expectations of House Members}, presented to them by the Evaluations director
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board
	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}
		The constitution should remain up to date with current practices.
\end{enumerate}

\asubsection{Responsibilities of the Chairman}
\begin{enumerate}
	\item To preside over Executive Board and House Meetings
	\item To exercise general supervision over the operations of the Executive Board
	\item To exercise general supervision over regular House activities
	\item To act as a liaison to the academic and administrative departments at RIT
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
	\item To cast tie-breaking vote in a split decision in an Executive Board vote
\end{enumerate}

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
	\item To preside over Evaluations Meetings
	\item To exercise general supervision over Evaluations operations
	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
	\item To oversee the Semi-Annual Evaluations of current House members
	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
	\item To prepare the House for Open Houses, tours, and special events
\end{enumerate}

\asubsection{Responsibilities of the Social Director}
\begin{enumerate}
	\item To preside over Social Meetings
		House members are encouraged to bring ideas for social events to the meetings for discussion.
	\item To exercise general supervision over Social operations
	\item To oversee the organization, initiation, and execution of House activities and events
	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
\end{enumerate}

\asubsection{Responsibilities of the Financial Director}
\begin{enumerate}
	\item To preside over Financial Meetings
		House members are encouraged to bring ideas for fund-raising activities to the meetings for discussion.
	\item To supervise financial administrators and transactions involving house projects
	\item To maintain financial and inventory records of House capital and assets
	\item To plan and enforce a House budget
	\item To oversee House finances and generation of House funds
	\item To publish a semesterly House financial statement
	\item To supervise the collection of semesterly House dues
	\item To oversee the planning and execution of fundraising events
\end{enumerate}

\asubsection{Responsibilities of the Research and Development Director}
\begin{enumerate}
	\item To preside over Research and Development Meetings
		House members are encouraged to bring ideas for projects to the meetings for discussion.
	\item To exercise general supervision over Research and Development operations
	\item To oversee the planning, organization and construction of technical projects for the House's benefit
	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment
	\item To provide seminars and tutorials to educate House members in technical areas
\end{enumerate}

\asubsection{Responsibilities of the House Improvements Director}
\begin{enumerate}
	\item To preside over House Improvements Meetings
	\item To exercise general supervision over the House Improvements operations
	\item To oversee the organization and construction of physical improvements to the House
	\item To oversee the general maintenance of the appearance of the House
\end{enumerate}

\asubsection{Responsibilities of the Operational Communications Director}
\begin{enumerate}
	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings
	\item To report the status of the House computer systems and network to the Executive Board and House members
\end{enumerate}

\asubsection{Responsibilities of the House History Director}
\begin{enumerate}
	\item To preside over House History Meetings
	\item To exercise general supervision over the House History operations
	\item To maintain, uphold, and promote house traditions
	\item To collaborate with the Social Director(s) to ensure that all the Active, Alumni, and Advisory Members are informed of upcoming events
	\item To oversee the production and distribution of a semi-annual newsletter
	\item To oversee the creation of a yearbook outlining House events for the year
\end{enumerate}

\asubsection{Responsibilities of the House Secretary}
\begin{enumerate}
	\item To ensure that minutes are recorded and posted for Executive Board Meetings
	\item To ensure that minutes are recorded and posted for House Meetings
	\item To oversee the maintenance of Executive Board records and documents
	\item To provide administrative assistance to the Executive Board
	\item To oversee the maintenance of the Activities Information Centers
	\item To record all votes cast during House Meetings and Open Executive Board Meetings
\end{enumerate}

\asubsection{Responsibilities of Ad Hoc Directorships}
\begin{enumerate}
	\item Ad-Hoc Directorships are responsible for the task for which they were created
	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director
\end{enumerate}

\asection{Qualifications}
\asubsection{Qualifications to be the Chairman, Evaluations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must reside on floor during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairman, should they be elected
\end{enumerate}
\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
\end{enumerate}
\asubsection{Qualifications to be the Operational Communications Director}
\begin{enumerate}
	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
	\item Candidates must be a current Active Member
	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position
\end{enumerate}

\asubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
\begin{enumerate}
\item Candidates must be Active Members
\end{enumerate}

### 2017-06-20 bylaws.tex
Removed all trailing whitespacs from .tex files
Fix Git Revision Insertion for Makefile (#108)

Fixed periods and capitalization

Add more instructions to readme

ran script to add periods to end of any bullet points

removed all periods at end of \item

removed periods

maunally edited the punctuation

ran script to add periods to end of any bullet points

removed all periods at end of \item

removed periods

maunally edited the punctuation

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\bylaw{Operations of the Evaluations Directorship}
\bsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for introductory members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\bsubsection{The Evaluation Period}
The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
\bsubsection{The Introductory Project}
Introductory members are expected to demonstrate initiative and an ability to work well in a group environment through the Introductory Project.
\bsubsection{Introductory Executive Board}
An Introductory Executive Board is elected by the introductory members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
The Introductory Executive Board consists of three members:
\begin{itemize}
	\item A President, who leads the project and acts as primary representative to House through weekly status reports at House Meeting.
	\item A Vice President, who assists the President in leadership and representation.
	\item A Treasurer, who manages the finances for the project.
\end{itemize}
Introductory Members also elect a Secretary to take notes, and any number of additional non-voting leaders may be elected to take on project-specific tasks.
\bsubsubsection{The Project}
The Project is an annual fundraising event that takes place in the first semester of the Introductory Process.
All of the proceeds go to a charity chosen in advance by the participants.
The Executive Board is encouraged to discuss the Project and following an open ballot Simple Majority Vote, may choose to intervene in the Introductory Project if the Project does not appear to fulfill requirements.
\bsubsubsection{Introductory Project Advisors}
The Evaluations Director may choose between one (1) and three (3) House members to be Introductory Project Advisors.
The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
\bsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
\begin{itemize}
	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
	\begin{itemize}
		\item Non-Resident members who have passed a Membership Evaluation
		\item Alumni members (not including Non-Resident Executive Board members)
		\item Honorary members
		\item Advisory members
	\end{itemize}
	\item A description of each Executive Board position, including:
	\begin{itemize}
		\item The responsibilities of the position
		\item The name(s) of the position’s member(s)
		\item The position’s weekly meeting time
	\end{itemize}
	\item A list of seven (7) annual House social events
	\item A list of seven (7) major House technical achievements
\end{itemize}
\bsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Be an active participant in the Introductory Project
\item Attend at least one House directorship meeting for each week of the process
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations.
\end{itemize}

@@

	\item The applicant submits an application to the Evaluations Director for review.
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
	\item The application materials are then reviewed at an Evaluations meeting.
	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an introductory member.

>>>>

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\bylaw{Operations of the Evaluations Directorship}
\bsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\bsubsection{The Evaluation Period}
The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
\bsubsection{The Introductory Project}
Introductory members are expected to demonstrate initiative and an ability to work well in a group environment through the Introductory Project.
\bsubsection{Introductory Executive Board}
An Introductory Executive Board is elected by the Introductory Members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
The Introductory Executive Board consists of three members:
\begin{itemize}
	\item A President, who leads the project and acts as primary representative to House through weekly status reports at House Meeting.
	\item A Vice President, who assists the President in leadership and representation.
	\item A Treasurer, who manages the finances for the project.
\end{itemize}
Introductory Members also elect a Secretary to take notes, and any number of additional non-voting leaders may be elected to take on project-specific tasks.
\bsubsubsection{The Project}
The Project is an annual fundraising event that takes place in the first semester of the Introductory Process.
All of the proceeds go to a charity chosen in advance by the participants.
The Executive Board is encouraged to discuss the Project and following an open ballot Simple Majority Vote, may choose to intervene in the Introductory Project if the Project does not appear to fulfill requirements.
\bsubsubsection{Introductory Project Advisors}
The Evaluations Director may choose between one (1) and three (3) House members to be Introductory Project Advisors.
The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
\bsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
\begin{itemize}
	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
	\begin{itemize}
		\item Non-Resident members who have passed a Membership Evaluation
		\item Alumni members (not including Non-Resident Executive Board members)
		\item Honorary members
		\item Advisory members
	\end{itemize}
	\item A description of each Executive Board position, including:
	\begin{itemize}
		\item The responsibilities of the position
		\item The name(s) of the position’s member(s)
		\item The position’s weekly meeting time
	\end{itemize}
	\item A list of seven (7) annual House social events
	\item A list of seven (7) major House technical achievements
\end{itemize}
\bsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Be an active participant in the Introductory Project
\item Attend at least one House directorship meeting for each week of the process
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
\end{itemize}

@@

	\item The applicant submits an application to the Evaluations Director for review
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members
	\item The application materials are then reviewed at an Evaluations meeting
	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
